Inferring generation-interval distributions from contact tracing data

### 2018-09-21 doc/network.tex
update

Given limited contact structure, a susceptible individual can be contacted multiple times;
infectious contacts give rise to infection only when the susceptible individual is contacted for the first time.
Then, the conditional kernel (conditional on the infection occuring) of an individual $a$ is given by
\begin{equation}
\hat{k}_a(\tau) = k_a(\tau) \exp \left(- \delta_a \int_0^\tau k_a(s) ds\right),
\end{equation}
where $\delta_a$ is the dilution.
The individual kernel, $k_a(s)$, measures the intrinsic infectiousness of an individual $a$,
whereas $\delta_a k_a(s)$ measures the infectiousness of an individual $a$ for a particular susceptible individual.
Then, the population-level conditional kernel is:
\begin{equation}
\hat{k}(\tau) = \int \hat{k}_a(\tau) dA,
\end{equation}
and the conditional generation-interval distribution, defined to be the distribution of times at which secondary infections occur from a single primary infector, is:
\begin{equation}
\hat{g}(\tau) = \frac{\hat{k}(\tau)}{\int \hat{k} \tau}.
\end{equation}
\swp{Need to say something about trapman!!!}

The difference between conditional and intrinsic generation-interval distribution can be best demonstrated by simulating stochastic infection processes on a small tree network, in which a single infected individual is connected to multiple susceptible individuals, with artificially high $\RR$ (Figure ??? to be made).
We observe that the distribution of realized generation times matches with the conditional generation-interval distribution, whereas the distribution of contact times matches with the intrinsic generation-interval distribution.
On the other hand, if a stochastic infection processes are simulated on a small homogeneous network (e.g., a household) with all else being equal, the distribution of generation times is even shorter than the effective generation intervals because a susceptible individual may be contacted by multiple infectors (and only the first contact gives rise to infection).
\jd{Let's think about how to explain this. In particular, the first one is where we have our correction that works \ldots}.
Hence, we expect there to be varying degrees of local depletion of susceptibles in a heterogeneous contact structure and the accurate measurement of generation interval will be more difficult.

\subsection{Spatial spread of an epidemic}

>>>>

\subsection*{Conditional kernel}

Given limited contact structure, a susceptible individual can be contacted multiple times;
infectious contacts give rise to infection only when the susceptible individual is contacted for the first time.
Then, the conditional kernel (conditional on the infection occuring) of an individual $a$ is given by
\begin{equation}
\hat{k}_a(\tau) = k_a(\tau) \exp \left(- \delta_a \int_0^\tau k_a(s) ds\right),
\end{equation}
where $\delta_a$ is the dilution.
The individual kernel, $k_a(s)$, measures the intrinsic infectiousness of an individual $a$,
whereas $\delta_a k_a(s)$ measures the infectiousness of an individual $a$ for a particular susceptible individual.
Then, the population-level conditional kernel is:
\begin{equation}
\hat{k}(\tau) = \int \hat{k}_a(\tau) dA,
\end{equation}
and the conditional generation-interval distribution, defined to be the distribution of times at which secondary infections occur from a single primary infector, is:
\begin{equation}
\hat{g}(\tau) = \frac{\hat{k}(\tau)}{\int \hat{k} \tau}.
\end{equation}
\swp{Need to say something about trapman!!! Maybe say this is a generalization of Trapman's work...? Is that too much?}

The difference between conditional and intrinsic generation-interval distribution can be best demonstrated by simulating stochastic infection processes on a small tree network -- a single infected individual is connected to multiple susceptible individuals but susceptibles are not connected with each other -- with artificially high $\RR$ (Figure ??? to be made).
We observe that the distribution of realized generation times matches with the conditional generation-interval distribution, whereas the distribution of contact times matches with the intrinsic generation-interval distribution.
On the other hand, if a stochastic infection processes are simulated on a small homogeneous network with all else being equal, the distribution of generation times is even shorter than the effective generation intervals because a susceptible individual may be contacted by multiple infectors (and only the first contact gives rise to infection).
\jd{Let's think about how to explain this. In particular, the first one is where we have our correction that works \ldots}.
Hence, we expect there to be varying degrees of local depletion of susceptibles in a heterogeneous contact structure and the accurate measurement of generation interval will be more difficult.
